Parallel multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-09-13 hpmoon-hpca.tex
Changes to pseudocode for issue #6

%\runninghead{Garc\'ia-S\'anchez et al.}
\runninghead{anonymous}
\title{Parallel Multi-objective optimization using co-evolutionary
  islands and search space overlapping}
% Why are you mixing caps and non-caps? - JJ

@@

>>>>

%\runninghead{Garc\'ia-S\'anchez et al.}
\runninghead{anonymous}
\title{Parallel multi-objective optimization using co-evolutionary
  islands and search space overlapping}
% Why are you mixing caps and non-caps? - JJ Pablo: fixed

@@

\textcolor{red}{Pseudo-code of the proposed algorithms is described in Algorithm \ref{fig:pseudo}.}

\begin{algorithm}[htb]

\begin{algorithmic}
\STATE \textit{//In each island $i$}
\STATE population $\gets$ initialisePopulation()
\STATE \textit{//Select which part modify in this island $i$}
\STATE section $\gets$ getComponentsToModify($i$)
\WHILE {stopping criterion not met}
    \STATE parents $\gets$ nsgaSelection(population)
    \FORALL{each 2 chromosome in parents}
    	\STATE \textit{//Crossovers only the part for island $i$}
    	\STATE children  $\gets$ crossover(parents,section)
    	\STATE offspring $\gets$ offspring + children
    \ENDFOR
    \FORALL{chromosome in offspring}
    	\IF {mutationProb $>$ random()}
    		\STATE \textit{//Mutates only the part for island $i$}
    		\STATE chromosome $\gets$ mutation(chromosome,section)
    		\STATE offspring $\gets$ chromosome + offspring
    	\ENDIF
    \ENDFOR
    \STATE population $\gets$ population + offspring

    \IF {time to migrate}
      \STATE migrants $\gets$ binaryTournament(population)
      \STATE remoteBuffer $\gets$ getRandomIslandBuffer()
      \STATE remoteBuffer.send(migrants)
    \ENDIF

    \IF {localBuffer.size $\neq$ zero}
      \STATE immigrants $\gets$ localBuffer.read()
      \STATE population $\gets$ population + immigrants
    \ENDIF
\ENDWHILE

\STATE sendIslandParetoFrontToServer()
\STATE \textit{Final Pareto Front from all islands is returned by the server}
\end{algorithmic}

\caption{Pseudo-code of the used EA in every island: a distributed NSGA-II algorithm }
\label{alg:EA}
\end{algorithm}
